SIRtesting

### 2020-11-09 note/R0_wrt_omega.tex
updated notes

Let us consider the linearization of $\Rnum$ around $\Rnum \approx 0$. \fady{As Ali pointed out to me, working with the linearization is okay since $\rho$ is the \text{daily per capita testing rate}, so it is expected to be fairly small. I was somehow thinking values of $\rho$ weren't gonna be small, but now I understand.}

@@

In order to check if this critical point is a minimum, we can check the sign of the second derivative. For convenience, let $Q = \frac{1-\eta_w}{1-\eta_t}\cdot\frac{\gamma}{\omega}\cdot\big(\frac{\gamma}{\omega}+\frac{W_i}{W_s}\big)$

>>>>

Let us consider the linearization of $\Rnum$ around $\rho \approx 0$. \fady{As Ali pointed out to me, working with the linearization is okay since $\rho$ is the \text{daily per capita testing rate}, so it is expected to be fairly small. I was somehow thinking values of $\rho$ weren't gonna be small, but now I understand.}

@@

In order to check if this critical point is a minimum, we can check the sign of the second derivative. For convenience, let $Q = \frac{1-\eta_w}{1-\eta_t}\cdot\frac{\gamma}{\omega}\cdot\big(\frac{\gamma}{\omega}+\frac{W_i}{W_s}\big)$ 
AGh: Call $Q$ something else to avoid confussion with the Q in eq 2.
